---
title: "vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Installation
You can install the released version of package RefTM from Github:
```javascript
devtools::install_github("zzchr1s/RefTM")
```

## A. RefTM-LDA workflow on scATAC data guided by aggregating single-cell data.

First, load package RefTM:

```{r}
library(RefTM)
```

### Input data

reference data: pseudo-bulk *forebrain_ref_data*. MG and OC cells are left when constructing the pseudo-bulk reference data to investigate the influence of incomplete reference data.
scCAS data: *forebrain_sc_data*

```{r}
sc_data <- forebrain_sc_data
ref_data <- forebrain_ref_data
cell_label <- forebrain_label_mat
```

### Modeling

```{r,eval=TRUE, results='hide', message=FALSE}
set.seed(2022)
result <- RefTM(sc_data, ref_data)
```

### Visualization

#### Visualization of latent topics obtained by LDA (no reference)

```{r,eval=TRUE, results='hide', message=FALSE}

result_LDA <- RefTM.LDA(t(sc_data), k = 10, k0 = 0, bulk_beta = NULL)
RetTM_tsne(result_LDA@gamma, cell_label)
```

#### Visualization of shared latent topics between reference data and scCAS data

```{r,eval=TRUE, results='hide', message=FALSE}
theta = RefTM_postprocess(result, k1 = 5)
RetTM_tsne(theta[, 1:k1], cell_label)
```

#### Visualization of unique latent topics in scCAS data

```{r,eval=TRUE, results='hide', message=FALSE}
RetTM_tsne(theta[, -c(1:k1)], cell_label)
```

#### Visualization of RefTM

```{r,eval=TRUE, results='hide', message=FALSE}
RetTM_tsne(theta, cell_label)
```

## B. RefTM-STM workflow on scATAC data guided by bulk data, with cell-specific covariates included.

First, load package RefTM:

```{r}
library(RefTM)
```

### Input data

reference data: pseudo-bulk *CLPLMPPMPP_ref_data*.
scCAS data: *CLPLMPPMPP_sc_data*.
covariate: *CLPLMPPMPP_donor_label*.


```{r}
sc_data <- CLPLMPPMPP_sc_data
ref_data <- CLPLMPPMPP_ref_data
donor_label <- CLPLMPPMPP_donor_label
cell_label <- CLPLMPPMPP_label_mat
```

### Modeling

```{r,eval=TRUE, results='hide', message=FALSE}
set.seed(2022)
result <- RefTM(sc_data, ref_data, workflow = "STM", covariate = as.factor(donor_label))
```

### Visualization

#### Visualization of RefTM without batch effect correction

```{r,eval=TRUE, results='hide', message=FALSE}
theta = RefTM_postprocess(result, k1 = 5, erase.BF = FALSE)
RetTM_tsne(theta, cell_label)
```

#### Visualization of RefTM with batch effect correction

```{r,eval=TRUE, results='hide', message=FALSE}
theta = RefTM_postprocess(result, k1 = 5)
RetTM_tsne(theta, cell_label)
```


###Cell clustering

```{r,eval=TRUE, results='hide', message=FALSE}
Seurat_louvain <- RA3::RA3_clustering(t(theta), length(unique(cell_label)))
```

## C. Motif enrichment analysis

### Input data

reference data: pseudo-bulk *cerebellum_ref_data*.
scCAS data: *cerebellum_sc_data*.


```{r}
sc_data <- cerebellum_sc_data
ref_data <- cerebellum_ref_data
cell_label <- cerebellum_label_mat
```

### Modeling

```{r,eval=TRUE, results='hide', message=FALSE}
set.seed(2022)
result <- RefTM(sc_data, ref_data)
```

###Cell clustering

```{r,eval=TRUE, results='hide', message=FALSE}
theta = RefTM_postprocess(result, k1 = 5)
Seurat_louvain <- RA3::RA3_clustering(t(theta), length(unique(cell_label)))
```

###
peaks <- cerebellum_peaks
louvain <- as.numeric(Seurat_louvain) 

