---
title: "vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Installation
You can install the released version of package RefTM from Github:
```javascript
devtools::install_github("zzchr1s/RefTM")
```

## A. RefTM on scATAC data guided by aggregating single-cell data

First, load package RefTM:

```{r}
library(RefTM)
```

### Input data

```{r}
sc_data <- forebrain_sc_data
ref_data <- forebrain_ref_data
cell_label <- forebrain_label_mat
```


### Modeling

```{r,eval=TRUE, results='hide', message=FALSE}
set.seed(2022)
result <- RefTM(sc_data,ref_data)
```

### Visualization

#### Visualization of shared latent topics between reference data and scCAS data

M3C::tsne()

#### Visualization of unique latent topics in scCAS data

M3C::tsne()

## B. RefTM on scATAC data guided by bulk data and including covariates

First, load package RefTM:

```{r}
library(RefTM)
```

### Input data

```{r}
sc_data <- CLPLMPPMPP_sc_data
ref_data <- CLPLMPPMPP_ref_data
cell_label <- CLPLMPPMPP_label_mat
```

### Modeling

```{r,eval=TRUE, results='hide', message=FALSE}
set.seed(2022)
result <- RefTM(sc_data,ref_data,workflow = "STM",covariate = as.numeric(as.factor(CLPLMPPMPP_label_mat)))
```








